Model of lens candidates from Space Warps CFHTLS

### 2016-07-13 paper2.tex
edits

@@

\begin{figure}
  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
  \caption{
      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
      bottom from left to right:
        reconstructed source in color,
        intensity (grayscale),
        count of lens plane pixels per source plane pixel,
        residual of orginal image to improved syntetic image in grayscale
    }
  \label{fig:synthimg}
\end{figure}

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as `$1+2+1$'.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.  These
  two panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.\todo{Fix distance factor in $\kappa$.}
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}

>>>>

The mass maps produced by current implementation of SpaghettiLens are
based on images of point-like features.  No information about extended
images is used, except in so far as they help the user identify images
of point-like features.  The synthetic images offered to users are
rudimentary, based on sources with conical light profiles.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
  \caption{Synthetic image with source-profile fitting in SW05
    (J143454.4+522850). Top-left: original image; top-right: synthetic
    image (coloured arcs) with lensing galaxy and unrelated objects in
    greyscale; bottom from left to right: reconstructed source in
    colour, intensity (greyscale), count of lens plane pixels per
    source plane pixel, residual of original image to synthetic
    image.}
  \label{fig:synthimg}
\end{figure}

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as `$1+2+1$'.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.
  (Figure~\figref{synthmig} in \S~\ref{subsec:sourcefit} shows a
  synthetic image from another model of the same system.) These two
  panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.\todo{Fix distance factor in $\kappa$.}
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}
